Baseline centering problem

### 2018-11-10 paper/advup_uniquesol.tex

The TD step is
\begin{equation}
\E_s \,\partial_\theta V(s)\left(
r(s,a)-b+\gamma V(s')-V(s)+(1-\gamma)V(\tilde s)-\alpha V(s)
\right)
\end{equation}
and its fixed point solves $r(s,a)-b+\gamma V(s')-V(s)+(1-\gamma)V(\tilde
s)-\alpha V(s)$ for all $s$. The unique solution for $V$ given $b$ is
\begin{equation}
V(s)=V^\pi(s)-\E_\rho V^\pi-\frac{b-(1-\gamma)\E_\rho V^\pi}{\alpha}
\end{equation}

@@

>>>>

The TD step is
\begin{equation}
\E_s \,\partial_\theta V(s)\left(
r(s,a)-b+\gamma V(s')-V(s)+(1-\gamma)V(\tilde s)-\alpha V(\tilde s)
\right)
\end{equation}
and its fixed point solves $r(s,a)-b+\gamma V(s')-V(s)+(1-\gamma)V(\tilde
s)-\alpha V(\tilde s)$ for all $s$. The unique solution for $V$ given $b$ is
\begin{equation}
V(s)=V^\pi(s)-\E_\rho V^\pi-\frac{b-(1-\gamma)\E_\rho V^\pi}{\alpha}
\end{equation}

@@

This means storing past states and recomputing the value function
at every time, not just storing past value functions.
